---
title: "How to study the effect of removing one list in the estimation of over-coverage"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```


In the electronic supplementary material of our paper, there is a simulation study where we discussed the different effects when removing registers in the estimation of our model. The link and the info for the paper follows:

- Mussino, E., Santos, B., Monti, A. et al. Multiple systems estimation
  for studying over-coverage and its heterogeneity in population
  registers. **Quality & Quantity** (2023).
  <https://doi.org/10.1007/s11135-023-01757-x>

Here we discuss the different steps of the simulation study and show how to reproduce the experiment. 

## Initial Setup 

For this simultation, we need to generate new population according to the same rules for every replication of the study. In the same way, we create 3 lists, $X$, $Y$ and $Z$, where the probability of being observed always follows the same function. For this experiment, we create 3 binary variables that are used separately in the probability function in each one of the lists.

The initial step is to generate the population, where we create one continuous and one categorical variable, although they will not be used for the study. The function just needs to create at least one variable of these types.

```{r}
library(overcoverage)
set.seed(42)
main_list <- create_population(size = 1e6,
                                 n_bin_var = 3, 
                                 n_cont_var = 1,
                                 n_cat_var = 1,
                                 c(0.5))
```

We assume that individuals will leave the country according to a logistic model and using `bin1` variable as the covariate to write this probability. Using the `create_presences` function from our package and considering only 2 years of observation, we have the following:

```{r}
true_presences <- create_presences(main_list, 
                                     formula_phi = ~ bin1,
                                     coef_values = c(2, -1),
                                     varying_arrival = TRUE,
                                     years = 2)
```

If $B_1$ represents `bin1` and $\phi$ is the probability of staying in the country (usually known as _surviving_, in the capture-recapture literature) each year, we considering the following logistic regression to calculate those probabilities

$$\log \begin{pmatrix}\frac{\phi}{1 - \phi} \end{pmatrix} = 2 - B_1,$$

With this equation, we are creating two probabilities of staying in the country, when $B_1 = 0$ or when $B_1 = 1$, which are calculated respectively as

$$\frac{\exp(2)}{1 + \exp(2)} = `r round(exp(2)/(1+exp(2)), 3)` \quad  \mbox{ and } \quad \frac{\exp(2 - 1)}{1 + \exp(2 - 2)} = `r round(exp(1)/(1+exp(1)), 3)`.$$

For each simulation step we also create 3 lists, $X$, $Y$ and $Z$, using the function `create_list_presences`.

```{r}
X <- create_list_presences(main_list, presences = true_presences, 
                           formula_prob = ~ bin1, 
                           coef_values = c(1.5, -0.5))
   
Y <- create_list_presences(main_list, presences = true_presences,
                           formula_prob = ~ bin2, 
                           coef_values = c(-0.5, -0.5))
  
Z <- create_list_presences(main_list, presences = true_presences,
                           formula_prob = ~ bin3, 
                           coef_values = c(-1.5, -0.5))
```

The argument `formula_prob` controls which variables are used to calculate the probability of being observed in each list. As we have said previously, we are considering the 3 different binary variables (`bin1`, `bin2` and `bin3`) separately for each list. The values in the argument `coef_values` are used in the logistic regression to generate the observation in each list. For instance, for list $X$ we are calculating the following

$$\log \begin{pmatrix}\frac{P(X = 1|B_1)}{1 - P(X = 1|B = 1)} \end{pmatrix} = 1.5 - 0.5 \cdot B_1,$$

which gives us estimated probabilities of `r round(exp(1.5)/(1+exp(1.5)), 3)` and  `r round(exp(1)/(1+exp(1)), 3)` for $B_1 = 0$ and $B_1 = 1$, respectively. 

Now we just need to recreate the scenarios where we use just part of tesse lists to estimate the over-coverage. For this particular toy example, the true value of over-coverage in the second year is given by

```{r}
n_present <- sum(true_presences[, 2])
true_oc <- 1 - n_present/nrow(main_list)
true_oc
```


## Removing lists and estimating over-coverage

At this step, we need to run the model to estimate the over-coverage and repeat the same procedure removing one of the lists, for instance. Considering all lists, we could run the following to estimate the over-coverage

```{r, eval=FALSE}
library(dplyr)
all_data <- 
  cbind(bin1 = main_list$bin1,
        bin2 = main_list$bin2,
        bin3 = main_list$bin3,
        X = X[, 2],
        Y = Y[, 2],
        Z = Z[, 2]) %>%
      as.data.frame()
    
freq_data <- all_data %>%
  group_by(bin1, bin2, bin3, X, Y, Z) %>%
  summarise(count = n())

freq_data <- freq_data %>%
  mutate(cens = ifelse(X == 0 &
                       Y == 0 &
                       Z == 0, TRUE, FALSE))

cens_ind <- which(freq_data$cens)
    
model <- overcoverage::oc_model(
      model_formula = count ~ bin1 * X + bin2 * Y + bin3 * Z, 
      freq_table = freq_data, censored = cens_ind)
```

Given this model, we can estimate our over-coverage as

```{r, echo=FALSE}
library(dplyr)
model <- readRDS("../../inst/example/vignette1.rds")
```

```{r}
mean(model$oc_estimates)
```

And a credible interval with 95% of probability can be calculated as 

```{r}
quantile(model$oc_estimates, c(0.025, 0.975))
```

A density plot of our estimates with the true value can be obtained with 

```{r}
library(ggplot2)

ggplot() + 
  theme_minimal() + 
  geom_density(aes(model$oc_estimates), adjust = 1.5, 
               fill = "royalblue") +
  geom_vline(aes(xintercept = true_oc, color = "True value"), linetype = 2) +
  labs(x = "Model-based over-coverage estimates") + 
  scale_color_manual(name = "", values = "red") + 
  theme(legend.position = "bottom")
```

To estimate the model without list $X$ for instance, we would need to run the following code. We need to change the censored observations index before running the code

```{r, eval=FALSE}
# removing X

freq_data_x <- all_data %>%
  group_by(bin1, bin2, bin3, Y, Z) %>%
  summarise(count = n())

freq_data_x <- freq_data_x %>%
  mutate(cens = ifelse(Y == 0 &
                         Z == 0, TRUE, FALSE))

cens_ind <- which(freq_data_x$cens)
    
model_x <- overcoverage::oc_model(
      model_formula = 
        count ~ bin1 + bin2 * Y + bin3 * Z, 
      freq_table = freq_data_x, 
      censored = cens_ind, 
      nsample = 60000, 
      n.burnin = 50000, 
      thin = 10)
```

```{r, echo=FALSE}
oc_estimates <- readRDS("../../inst/example/vignette2.rds")
model_x <- as.data.frame(oc_estimates)
```


Now, our mean posterior estimates and 95% credible intervals will be given by

```{r}
mean(model_x$oc_estimates)
```

```{r}
quantile(model_x$oc_estimates, c(0.025, 0.975))
```

## Simulation setup

For the simulation, we will consider the same data set for every replication of the study and we estimate over-coverage with all lists and removing one list at a time. In order to make the simulations easier, we write a function to run one replicate, where we create one data set and return all the different over-coverage estimates.

```{r, eval=FALSE}
sim_mse <- function(seed){
  
  set.seed(seed)

  n_years <- 2
  
  ## Creating population
  main_list <- create_population(size = 1e6,
                                 n_bin_var = 3, 
                                 n_cont_var = 1,
                                 n_cat_var = 1,
                                 c(0.5))
  
  true_presences <- create_presences(main_list, 
                                     formula_phi = ~ bin1,
                                     coef_values = c(2, -1),
                                     varying_arrival = TRUE,
                                     years = n_years)
  
  # calculating the true over-coverage at year 2.
  true_oc <- 1 - true_presences[, n_years] / nrow(main_list)
  
  X <- create_list_presences(main_list, 
                             presences = true_presences,
                             ~ bin1, 
                             c(1.5, -0.5))
   
  Y <- create_list_presences(main_list, 
                             presences = true_presences,
                             ~ bin2, 
                             c(-0.5, -0.5))
  
  Z <- create_list_presences(main_list, 
                             presences = true_presences,
                             ~ bin3, 
                             c(-1.5, -0.5))
  
  new_data <- 
  cbind(bin1 = main_list$bin1,
        bin2 = main_list$bin2,
        bin3 = main_list$bin3,
        X = X[, 2],
        Y = Y[, 2],
        Z = Z[, 2]) %>%
      as.data.frame()
  
  sim_cases <- list()
  
  freq_data <- new_data %>%
    group_by(bin1, bin2, bin3, X, Y, Z) %>%
    summarise(count = n())
  
  freq_data <- freq_data %>%
    mutate(cens = ifelse(X == 0 &
                         Y == 0 &
                         Z == 0, TRUE, FALSE))
  
  cens_ind <- which(freq_data$cens)
  
  sim_cases[[1]] <- oc_model(
    count ~ bin1 * X + bin2 * Y + bin3 * Z,
    freq_table = freq_data,
    cens = cens_ind, 
    nsample = 60000,
    n.burnin = 50000, 
    thin = 10)
  
  freq_data_x <- new_data %>%
    group_by(bin1, bin2, bin3, Y, Z) %>%
    summarise(count = n())
    
  freq_data_x <- freq_data_x %>%
      mutate(cens = ifelse(Y == 0 &
                           Z == 0, TRUE, FALSE))
    
  cens_ind_x <- which(freq_data_x$cens)
    
  sim_cases[[2]] <- oc_model(
    count ~ bin1 + bin2 * Y + bin3 * Z,
    freq_table = freq_data_x,
    cens = cens_ind_x, 
    nsample = 60000,
    n.burnin = 50000, 
    thin = 10) 
  
  freq_data_y <- new_data %>%
    group_by(bin1, bin2, bin3,
             X, Z) %>%
    summarise(count = n())
    
  freq_data_y <- freq_data_y %>%
    mutate(cens = ifelse(X == 0 &
                         Z == 0, TRUE, FALSE))
    
  cens_ind_y <- which(freq_data_y$cens)
    
  sim_cases[[3]] <- oc_model(
    count ~ bin1 * X + bin2 + bin3 * Z,
    freq_table = freq_data_y,
    cens = cens_ind_y, 
    nsample = 60000,
    n.burnin = 50000, 
    thin = 10) 

  freq_data_z <- new_data %>%
      group_by(bin1, bin2, bin3, X, Y) %>%
      summarise(count = n())
    
  freq_data_z <- freq_data_z %>%
    mutate(cens = ifelse(X == 0 & 
                           Y == 0, TRUE, FALSE))
    
  cens_ind_z <- which(freq_data_z$cens)
    
  sim_cases[[4]] <- oc_model(
    count ~ bin1 * X + bin2 * Y + bin3,
    freq_table = freq_data_z,
    cens = cens_ind_z, 
    nsample = 60000,
    n.burnin = 50000, 
    thin = 10)
  
  list(
    relat_mean = sapply(sim_cases, function(a) mean(a$oc_estimates)/true_oc),
    relat_q = sapply(sim_cases, function(a) 
      quantile(a$oc_estimates, c(0.025, 0.975))/true_oc))

}
```

Now we can write a function to call the same function a number of times and record their results. We can do that with `lapply` or `purrr::map`, but here we will use the former, obtaining 50 replicates. 

```{r, eval=FALSE}
simulations <- lapply(1:50, sim_mse)
```

If we use a machine with multiple cores and a compatible operational system, we can put this simulation study with multiple cores. For instance, using the package `parallel`, we could run the following defining the number of cores with the argument `mc.cores`. 

```{r, eval=FALSE}
simulations <- parallel::mclapply(1:50, sim_mse, mc.cores = 5)
```

## Analysis of the results

## Final discussion

